{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2024-12-29 Notebook LaTEX/Proposal/main.tex
>w<, changes

    \subsection{Nesterov's Estimating sequence technique}
        \todoinline{\noindent
            Do the following: 
            \begin{enumerate}
                \item What is Nesterov's estimating sequence. 
                \item How is it used to derive the algorithm and convergence rate of algorithm. 
                \item Where is it used and why is it important here. 
            \end{enumerate}
        }
        \todoinline{
            Examples
            \begin{enumerate}
                \item Example estimating sequence. 
            \end{enumerate}
        }

>>>>

    \subsection{Nesterov's estimating sequence technique}
        \todoinline{\noindent
            Do the following: 
            \begin{enumerate}
                \item What is Nesterov's estimating sequence. 
                \item How is it used to derive the algorithm and convergence rate of algorithm. 
                \item Where is it used and why is it important here. 
            \end{enumerate}
        }
        \todoinline{
            Examples
            \begin{enumerate}
                \item Example estimating sequence. 
            \end{enumerate}
        }
        The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counter parts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
        Further discussions would require giving an example of estimating sequence first. 
        The definition follows gives an example of an estimating sequence. 
        \begin{definition}[Nesterov's estimating sequence]
